---
title: 'Homework #3: SDGB-7844'
author: "Qing Chen"
fordham_id_number: "A16799160"
fordham_email: "qchen97@fordham.edu"
date: "3/28/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 1. At what level (State, County, City) is the American Community Survey data available? How is this different than the deccenial census?

```{r}
library(maptools)
library(RColorBrewer)
library(rgdal)
library(sp)
library(maps)
library(tidyverse)
library(tidycensus)
library(tidyr)
library(ggplot2)
library(dplyr)
library(leaflet)

'"State" and "County" levels are availiable for ACS.
It is different from deccenial census, becuase get_acs() can be used
in more geography than get_decennial, such as "us","region" and "division."'

```

### 2. What variable and variable codes are available to describe race and ethnicity in the US Census? Describe how these variables are represented in the data (Variables: B2001_001-B2001_006 & B03002_001- B03002_002 & B03002_012).
```{r}

v15 <- load_variables(2016, "acs5", cache = TRUE)
'
# Race #
B02001_001 :Total Race
B02001_002 :White Alone Race
B02001_003 :Black or African American alone
B02001_004 :American Indian and Alaska Native alone
B02001_005 :Asian alone
B02001_006 :Native Hawaiian and Other Pacific Islander alone

# Ethnicity #
B03002_001 :Total
B03002_002 :Not Hispanic or Latino
B03002_012 :Hispanic or Latino
'


```

### 3. How does the American Community Survey define race and ethnicity? Is this important information to report under assumptions for your analysis?
```{r}

# Race: The Census Bureau defines race as a person's self-identification with one or more social groups.An individual can report as White, Black or AfricanAmerican, Asian, American Indian and Alaska Native,Native Hawaiian and Other Pacific Islander, or someother race. Survey respondents may reportmultiple races.
# 
# Ethnicity: it determines whether a person is of Hispanic origin or not. For this reason, ethnicity is broken outin two categories, Hispanic or Latino and NotHispanic or Latino. Hispanics may report as any race
# 
# It is important information to report, because the analysis assumption has the same definition as ACS, whose dataset, therefore, can be used.

```

### 4. Does the American Community Survey provide the margin of error for their estimates of the proportion
of the prevalence of each race and ethnicity? How might this impact the validity of our results?


```{r}
 
'Yes, ACS provide the margin of error (moe) for estimates. as the ACS is based on an annual sample of around 3 million households.
Also, the margin of error expresses the maximum expected difference between the true population parameter and a sample estimate of that parameter. So the lower margin of error, the higher validaty of result be.'

```

### 5. Use the tidycensus API to assign the race and ethnicity data for New York, New Jersey and Connecticut
(at the County level) to a data frame.

```{r}
# New York

var_re <- c('B02001_001','B02001_002', 'B02001_003','B02001_004','B02001_005','B02001_006','B03002_001','B03002_002','B03002_012')
NY <- get_acs(geography = "county", variables =var_re, state='NY')

NJ <- get_acs(geography = "county", variables =var_re, state='NJ')

CT <- get_acs(geography = "county", variables =var_re, state='CT')

class(NY)
```


## Computing The USA Today Diversity Index

```{r}
# Step1
US <- get_acs(geography = "county", variables =var_re, geometry = TRUE)


drop <- c('moe')
us_nomoe <- US[,!(names(US)%in%drop)]
rect_data <- us_nomoe %>% 
  spread(variable, estimate)

colnames(rect_data)[3:8] <- c('Total Race','White','Black','American Indian','Asian','Other Race')

colnames(rect_data)[9:11] <- c('Total Ethnicity','Not Hispanic or Latino','Hispanic or Latino')

# caculate racial porprotion for each county 
race <- data.frame("County" = rect_data[,2])
for (i in 4:8) {
  coname = colnames(rect_data)[i]
  race <- cbind(race, (rect_data[,i]/rect_data[,3])[,1])
  colnames(race)[i-1] <- coname
}

# Step2
# Caculate the probability that two people are of the same race
rsum <- rep(c(0),times = 3220)
for (i in 3:6) {
  rsum <- rsum + (race[,i])^2
  print(rsum[1:10]) # for check
}

hw3 <- cbind(race,rsum)
colnames(hw3)[8] <- '2_same_race_prob'

# Step3
ethnicity <- data.frame("County" = rect_data[,2])
for (i in 10:11) {
  coname = colnames(rect_data)[i]
  ethnicity <- cbind(ethnicity, (rect_data[,i]/rect_data[,9])[,1])
  colnames(ethnicity)[i-7] <- coname
}

# the probability that any two people will be Hispanic or not
esum <- rep(c(0),times = 3220)
for (i in 3:4) {
  esum <- esum + (ethnicity[,i])^2
  print(esum[1:10]) # for check
}

hw3 <- cbind(hw3,ethnicity[3:4],esum)
colnames(hw3)[11] <- '2_same_ethnicity_prob'

# Step4
# calculate whether two people are the same on both measures
both_prob <- esum * rsum
hw3 <- cbind(hw3,both_prob)

# Step5
# calculate diveristy index
diveristy_inx <- (1-both_prob)*100
hw3 <- cbind(hw3,diveristy_inx)

```

### 6. Create a histogram of USA Today Diversity Index values. Describe the shape of the histogram in
statistical terms (Hint: skewness).

#### This histogram chart shows that the frequency of different range of diversity index.  "10-20" has the highest frequency (about 700).
As for the shape, it is asymmatry and its distribution is skewed to the right ,which means that the mean of diversity index is less than the mode
```{r}

hist(hw3$diveristy_inx, main = "Histogram: \n USA Diversity Index", 
     xlab = "Diversity Index", ylab = "Frequency", 
     col = "firebrick", density = 75,
     angle = 50, border = "black")
```

### 7. Create a visualization which compares the top 10 counties and their diversity index value using ggplot2.
```{r}

county_separated <- hw3 %>% 
  separate(County.NAME, 
           into=c("County", "State"), 
           sep=",")

county_separated <- county_separated %>% 
  separate(County, 
           into=c("County", "County2"), 
           sep=" County")
county_separated <- county_separated[,!(names(county_separated)=='County2')]

top10di <- county_separated %>%
  select(diveristy_inx,County) %>%
  arrange(desc(diveristy_inx))

ggplot(top10di[1:10,], aes(County,diveristy_inx,fill = County), xlab(NULL))+
  geom_col()+ labs(fill = "County",title = 'Top 10 Diversity Index') + xlab("County") + ylab('Diversity Index')

```

### 8. Using the leaflet mapping library for R (or another mapping library of your choice), visualize the USA Today Diversity Index by county for New York, New Jersey and Connecticut.
```{r}

NYDI <- filter(county_separated, State == " New York")
NJDI <- filter(county_separated, State == " New Jersey")
CTDI <- filter(county_separated, State == " Connecticut")

```

### 10. Does there appear to be any relationship between geography and diversity? Which state appears to be
the most diverse?

#### Obviously, in general situation, the north of the three states has low diversity index(around 0~30). Also, mostly, counties with high diversity index are near sea areas.
Compared with the other two states, New Jersey appreas to be the higest diversity index state.

```{r}

NY_NJ_CT_DI <- rbind(NYDI,NJDI,CTDI)
NY_NJ_CT_DI1 <- NY_NJ_CT_DI[,4:13]
NY_NJ_CT_DI <- NY_NJ_CT_DI[, !(names(NY_NJ_CT_DI)%in%names(NY_NJ_CT_DI1))]

NNCmap <- leaflet(data = NY_NJ_CT_DI$County.geometry)
NNCpal <- colorNumeric(
  palette = "Reds",
  domain = NY_NJ_CT_DI$diveristy_inx)
NNClabels <- sprintf(
  "<strong>%s</strong><br/>Diversity Index %g",
  NY_NJ_CT_DI$County, NY_NJ_CT_DI$diveristy_inx
) %>% lapply(htmltools::HTML)

NNCmap %>%
  addPolygons(
  fillColor = NNCpal(NY_NJ_CT_DI$diveristy_inx),
  weight = 2,
  opacity = 1,
  color = "white",
  dashArray = "3",
  fillOpacity = 0.7,
  highlight = highlightOptions(
    weight = 5,
    color = "#666",
    dashArray = "",
    fillOpacity = 0.7,
    bringToFront = TRUE),
  label =NNClabels,
  labelOptions = labelOptions(
    style = list("font-weight" = "normal", padding = "3px 8px"),
    textsize = "15px",
    direction = "auto"))%>%
  addLegend("bottomright", pal = NNCpal, values = NY_NJ_CT_DI$diveristy_inx,
    title = "Diversity Index")


```


### 11. Create a new data frame using the tidycensus API with data on median household income by county
for New York, New Jersey and Connecticut. Join this data together with the data from New York
County. Use ggplot2 (or another visualization library) to visualize the USA Today Diversity Index
value and median household incomeon the same plot (Hint: try facet wrap!).

#### The scatter plot shows that the diversity index is positivly correlated to the median income for New York and Connecticut. In New Jersey, there is a negative relationship between those two factors.

```{r}
median_income <- get_acs(geography = 'county', variables = 'B06011_001', geometry = TRUE, state=c('NY','NJ','CT'))

income_no_moe <- median_income[,!(names(median_income)%in%drop)]
income_rect_data <- income_no_moe %>% 
  spread(variable, estimate)

income_separete <- income_rect_data %>% 
  separate(NAME, 
           into=c("County", "State"), 
           sep=",")

income_separete <- income_separete %>% 
  separate(County, 
           into=c("County", "County2"), 
           sep=" County")
income_separete <- income_separete[,!(names(income_separete)=='County2')]


join_income_DI <- merge(x=income_separete,y=NY_NJ_CT_DI, by = 'County', all.x = TRUE)
colnames(join_income_DI)[3]<- 'State'


a <- ggplot (join_income_DI, aes(x=B06011_001, y=diveristy_inx,color = State)) + geom_point(shape=1)+ geom_smooth(method = "lm")+
  ggtitle("Scatter Plot: \n USA Diversity Index vs Median Income" )+ labs(x = "Median Income", y= "Diveristy Index")

a + facet_grid(. ~State  )
```